|

### 2023-02-05 manuscript/manuscript.Rmd
done for today

\begin{center}
\textbf{Keywords:} Quality of Life, Randomized Controlled Trials,\\ Truncated Outcomes, Semi-Continuous Outcomes, Empirical Likelihood
\end{center}

@@

```{r, echo = FALSE, fig.width = 8, fig.height = 3, fig.cap="\\label{fig:application}Histograms of days alive without life support from the The COVID-STEROID2 trial stratified by treatment dosis (left, middle) and simultaneous confidence regions based on the semi-parametric likelihood ratio test (right).", fig.pos="htbp"}
par(mfrow=c(1,3), mgp=c(2.2,1,0), mar=c(3.2, 3.5, 2, 0))
hist(subset(d, d$allocation)$dawols28, xlim=c(0,30),
     main="Low dose", ylim=c(0,55), 10, col="gray70", border="gray90",
     cex.axis=1.2, cex.main=1.5, cex.lab=1.5, ylab="",
     xlab="Days alive without life support")
hist(subset(d, !d$allocation)$dawols28, 10, xlim=c(0,30),
     main="High dose", ylim = c(0,55), col="gray70", border="gray90",
     cex.axis=1.2, cex.main=1.5, cex.lab=1.5, ylab="",
     xlab="Days alive without life support")
image(sCI$muDelta, sCI$logORdelta, sCI$surface,
     col = rev(fields::tim.colors(256)), useRaster = TRUE,
     xlab="Difference in means",
     ylab="log OR",
     cex.axis=1.2, cex.main=1.5, cex.lab=1.5)
points(m_SPLRT$muDelta, log(m_SPLRT$alphaDelta), pch = 19, cex = 1.5)
contour(sCI$muDelta, sCI$logORdelta, sCI$surface, add = TRUE, 
        levels = stats::qchisq(0.99, 2), lwd = 1, labels = 0.99, lty=1)
contour(sCI$muDelta, sCI$logORdelta, sCI$surface, add = TRUE, 
        levels = stats::qchisq(0.95, 2), lwd = 1, labels = 0.95, lty=1)
contour(sCI$muDelta, sCI$logORdelta, sCI$surface, add = TRUE, 
        levels = stats::qchisq(0.8, 2), lwd = 1, labels = 0.8, lty=1)
contour(sCI$muDelta, sCI$logORdelta, sCI$surface, add = TRUE, 
        levels = stats::qchisq(0.5, 2), lwd = 1, labels = 0.5, lty=1)
title("Confidence regions", cex.main=1.5)
abline(v = 0, lty=2)
abline(h = 0, lty=2)
```

>>>>

\begin{center}
\textbf{Keywords:} Quality of Life, Randomized Controlled Trials,\\ Truncated Outcomes, Semi-Continuous Distributions, Empirical Likelihood
\end{center}

@@

```{r, echo = FALSE, fig.width = 8, fig.height = 3, fig.cap="\\label{fig:application}Histograms of days alive without life support from the The COVID-STEROID 2 trial stratified by treatment dosis (left, middle) and simultaneous confidence regions based on the semi-parametric likelihood ratio test (right).", fig.pos="htbp"}
par(mfrow=c(1,3), mgp=c(2.2,1,0), mar=c(3.2, 3.5, 2, 0))
hist(subset(d, d$allocation)$dawols28, xlim=c(0,30),
     main="Low dose", ylim=c(0,55), 10, col="gray70", border="gray90",
     cex.axis=1.2, cex.main=1.5, cex.lab=1.5, ylab="",
     xlab="Days alive without life support")
hist(subset(d, !d$allocation)$dawols28, 10, xlim=c(0,30),
     main="High dose", ylim = c(0,55), col="gray70", border="gray90",
     cex.axis=1.2, cex.main=1.5, cex.lab=1.5, ylab="",
     xlab="Days alive without life support")
image(sCI$muDelta, sCI$logORdelta, sCI$surface,
     col = rev(fields::tim.colors(256)), useRaster = TRUE,
     xlab="Difference in means",
     ylab="log OR",
     cex.axis=1.2, cex.main=1.5, cex.lab=1.5)
points(m_SPLRT$muDelta, log(m_SPLRT$alphaDelta), pch = 19, cex = 1.5)
contour(sCI$muDelta, sCI$logORdelta, sCI$surface, add = TRUE, 
        levels = stats::qchisq(0.99, 2), lwd = 1, labels = 0.99, lty=1)
contour(sCI$muDelta, sCI$logORdelta, sCI$surface, add = TRUE, 
        levels = stats::qchisq(0.95, 2), lwd = 1, labels = 0.95, lty=1)
contour(sCI$muDelta, sCI$logORdelta, sCI$surface, add = TRUE, 
        levels = stats::qchisq(0.8, 2), lwd = 1, labels = 0.8, lty=1)
contour(sCI$muDelta, sCI$logORdelta, sCI$surface, add = TRUE, 
        levels = stats::qchisq(0.5, 2), lwd = 1, labels = 0.5, lty=1)
title("Confidence regions", cex.main=1.5)
abline(v = 0, lty=2)
abline(h = 0, lty=2)
```
